% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=4.7in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Michael Van Veen\\[12pt]} % the \\[12pt] adds a blank line after name
\address{{\bf Current Location} \\ Encinitas, CA 92024}
\address{{\bf Contact Information} \\ Mobile: \space \space (724) VAN-VEEN \\Email: \space \space \space michael@mvanveen.net\\Website: \space mvv.io\\
Github: \space \space github.com/mvanveen} 
\begin{resume} 
 
\section{Experience}

  {\bf Software Engineer,} Zest Finance \hfill July 2017 - Present\\
  Software engineer supporting loan assessment infrastructure.  Start date is July 31st, 2017 \\

  {\bf Software Engineering Consultant,} Self-Employed   \hfill Feb 2016 - July 2017\\
    Currently offering full-stack software engineering consulting services. \\
    Current / Previous projects include:
    \begin{itemize}
    \item {\bf Terranodo}, Python/GIS software consultant.  Implemented new features on Django application, debugged  existing celery queue, worked on Docker/Jenkins continuous integration pipeline.
    \item {\bf Growthbot.io}, Principal engineer.  Built out Slack bot SaaS product MVP using Flask, SQLAlchemy, Celery, PostgreSQL and Redis.  Worked directly with CEO from early ideation and managed design and engineering resources.  Managed engineering resource implementing front-end buit in React Redux.
    \item {\bf Fight For the Future}, Full-stack software consultant.  Building out a video recording widget for the July 12th Battle for the Net day of action around net neutrality.  Leveraging Ziggeo API for video recording and playback functionality.  Backend is written using Flask, Celery, Redis and RabbitMQ.  Front-end is written using Bootstrap3 and jQuery.
    \end{itemize}
  {\bf Backend Software Engineer,} Manifest Commerce \hfill Nov 2014 - Feb 2016\\
  Backend software engineer.
  \begin{itemize}
    \item Co-authored and launched rewrite of Manifest's ad platform backend including early alerting and release management.  Project was built on AWS using technologies such as Python, Celery, Flask, SQLAlchemy, PostgreSQL, and RabbitMQ.
    \item Supported and scaled platform from first test ad to over \$1M revenue / month and majority of client spend.
    \item Maintained ad bidding engines and provided system technical support including on-call duties.
    \item Authored the Facebook Ad API web service layer of new ad platform
    \item Primary technical resource for client importer onboarding.
  \end{itemize}

  {\bf Software Engineering Consultant,} Self-Employed   \hfill Nov 2012 - Nov 2014\\
  Consulted for a variety of consultants.  Clients/projects included:
  \begin{itemize}
    \item {\bf Matterport}, Django Consultant (2014)
    \item {\bf Manifest Commerce}, Client importer consultant (2013-2014)
    \item {\bf Real Pie Media}, Godofwar.com tech lead.  Built out front-end and backend features including responsive mobile UI support and an admin panel.  Managed inter-team localization effort across over 17 languages.(2013)
    \item {\bf Joystick Interactive}, Google Social Voting App backend dev (2012)
  \end{itemize}

  {\bf Software Engineer,} Getaround \hfill Nov 2010 - Sept 2012, \\
  Full-stack Software Engineer and former intern.  Supported early getaround rental engine and web platform as member of early engineering team.
  \begin{itemize}
   \item Primary author on services for event-based emails, couponing, car unlocks.  Backend systems were Python 2.5/2.7 on Google App Engine.
    \item Built and maintained a custom GitHub pull request-based CI platform.
    \item Co-authored initial web integration test suite with Director of Eng.
  \end{itemize}


{\bf Student Intern,} Jet Propulsion Laboratory \hfill June 2009 - Sept 2009, \\
 Developed a set of code rule compliance checkers in Python and C++ under the supervision of Dr. Gerard Holzmann in the Laboratory for Reliable Software (LaRS).  Code checkers targeted rules defined in the NASA/JPL C coding standard.
 \begin{itemize}
 \item Employed the visitor pattern to create custom static-analysis tooling in Python and bash shell scripting.
 \item Developed Coverity Extend extensions in C++
 \end{itemize}

 {\bf Student Intern,} Jet Propulsion Laboratory \hfill June 2007 - Sept 2007, \\
 \makebox[3.27in]{\hfill} June 2008 - Aug 2008 \\ 
 Co-developed a web application which assisted Systems Engineering team in management of command and telemetry dictionaries.
 \begin{itemize}
 \item Developed application frontend. Maintained and updated database backend.
 \item Extended command/telemetry dictionary importation and exportation processes
 \item Implemented user permissions and authorization framework hooked up to organization LDAP
 \end{itemize} 

 {\bf Co-founder,} Zooomr, Inc. \hfill Oct 2005 - June 2007 \\
  Zooomr was a web 2.0  photo sharing application supporting features such as OpenID authentication, mobile upload, geotagging, trackbacks, comments, as well as localization in over 20 languages (now defunct).

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
   \underline{Languages:} & C, C++, Python, PHP, \LaTeX, SQL, HTML, JS , CSS, Golang (beginner) \\
   \underline{Platforms} & Linux, UNIX, Mac OS X, Google App Engine, Amazon EC2, Heroku\\
   \underline{APIs} & Google, GitHub, Dropbox, Facebook, MailChimp, MixPanel, Twitter to name a few\\
   \underline{Software} & vim, git, Adobe Photoshop, Microsoft Office, OpenOffice.org, Apache Web Server, SSHD\\
 \end{tabular}

\section{Education} 
{\bf University of California, Davis}  \hfill 2013\\
Bachelors of Science \\
Major: Computer Science \\

\section{Interests}
Music (guitar, percussion, harmonica, ableton), Photography, Cycling, Reading, Camping/Backpacking, Computer Art

\end{resume} 
\end{document} 
